A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-08 latex/main.tex
Updates from Overleaf
Update for Zenodo release
Closes #961

\item The sequences alignments in VCF Zarr format have been deposited at Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The ARG in tskit format has been deposited at Zenodo and is publicly available at \url{https://zenodo.org/records/16313750}.
\item The complete configuration file for running sc2ts to build the ARG above is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original source code of sc2ts is publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts/}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

%%%  Use this section to acknowledge contributions
%%%  from non-authors and list funding sources,
%%%  including grant numbers.

>>>>

\item The ARG in tskit format has been deposited at Zenodo and is publicly
available at \url{https://zenodo.org/records/17558489}. The UShER tree
in tskit format is also available, as well as the intersection files.
\item The sequences alignments in VCF Zarr format have been deposited at 
Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The complete configuration file for running sc2ts to build the ARG above is 
publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly 
available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original code of sc2ts is publicly available on 
GitHub at \url{https://github.com/jeromekelleher/sc2ts/}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

%%%  Use this section to acknowledge contributions
%%%  from non-authors and list funding sources,
%%%  including grant numbers.
We would like to thank Jotun Hein for helpful comments on the manuscript.
